Kernel Smoothing And Heat Equation

### 2020-11-03 latex/draft.tex
updated meeting notes

\begin{itemize}
\item 10/27/2020. We reviewed Dr. Qiu's code/documentation. Todos:
  \begin{enumerate}
  \item Compare our old code with Dr. Qiu's new code one more time.
  \item Try to implement the circular smoother (at least for the fixed bandwidth case).
  \item We've already studied the mathematical connections between the classical (homogeneous) heat equation and Gaussian kernel smoothing. We need to document this important connection in this document.
  \item We need to think: what is the mathematical connection between \emph{adaptive Gaussian kernel smoother} and \emph{inhomogeneous} heat equation?  Rationale: we've already derived (based on large sample theory) the ``optimal'' variable bandwidth for kernel smoother. If the kernel smoother is equivalent to an inhomogeneous differential equation, it means that we can then use an efficient numerical DE solver (e.g., those based on finite element method) to do kernel smoothing, especially for multi-dimensional cases.
  \item In the long run, we need to develop a practical estimation procedure for $x(t)$ and $\sigma^{2}(t)$, better with some model selection procedure so the entire estimation procedure can be automated.
  \item Multi-dimensional!! (a) the curse of dimensionality, (b) much more complicated boundary to deal with.
  \end{enumerate}
\end{itemize}

>>>>

\begin{itemize}
% 11/03/2020  
\item 11/03/2020. We implemented circular smoother on both fixed bandwidth and adaptive bandwidth scenarios; and did the corresponding simulation. We notice adaptive bandwidth cannot beat the optimal fixed bandwidth. Fixed bandwidth achieve the smallest MSE in our $y=\sin(x)$ setting. 
\begin{verbatim}
           euclidean   circular
Adaptive  0.19821445 0.19821445
logb=-3   1.00313133 1.00313133
logb=-2.4 1.00313133 1.00313133
logb=-1.8 1.00313133 1.00313133
logb=-1.2 0.11346202 0.11227971
logb=-0.6 0.02875581 0.02717735
logb=0    0.08004308 0.08145240
logb=0.6  0.44585526 0.52684029
logb=1.2  0.49326980 0.50454607
logb=1.8  0.50018979 0.50094139
logb=2.4  0.50068896 0.50068896
logb=3    0.50068896 0.50068896
\end{verbatim}

TODOLIST:
  \begin{enumerate}
    \item 
    \item 
  \end{enumerate}

% 10/27/2020  
\item 10/27/2020. We reviewed Dr. Qiu's code/documentation. Todos:
  \begin{enumerate}
  \item Compare our old code with Dr. Qiu's new code one more time.
  \item Try to implement the circular smoother (at least for the fixed bandwidth case).
  \item We've already studied the mathematical connections between the classical (homogeneous) heat equation and Gaussian kernel smoothing. We need to document this important connection in this document.
  \item We need to think: what is the mathematical connection between \emph{adaptive Gaussian kernel smoother} and \emph{inhomogeneous} heat equation?  Rationale: we've already derived (based on large sample theory) the ``optimal'' variable bandwidth for kernel smoother. If the kernel smoother is equivalent to an inhomogeneous differential equation, it means that we can then use an efficient numerical DE solver (e.g., those based on finite element method) to do kernel smoothing, especially for multi-dimensional cases.
  \item In the long run, we need to develop a practical estimation procedure for $x(t)$ and $\sigma^{2}(t)$, better with some model selection procedure so the entire estimation procedure can be automated.
  \item Multi-dimensional!! (a) the curse of dimensionality, (b) much more complicated boundary to deal with.
  \end{enumerate}
\end{itemize}
